A thesis draft

### 2018-11-21 res/sections/25-TestsResponsiveness.tex
Fix dictionary

Regarding the overall system responsiveness, a metric we considered worth to 
test was the VNF start up time in a docker environment versus one virtualized 
through a common virtual machine system (in this case Virtual Box was chosen). 
To make this simulation as fair as possible, we used the same node (an 
Openstack VM vith 32GB of RAM, 8 vCPU and solid state storage) and used the 
same ``boot sequence'' for both the VNFs: first we launched the Astaire 
framework, ensuring its availability to process data and then we notified the 
test machine of the successful boot. The start-up time was measured from the 
beginning of the start-up command (\verb!docker run! for Docker and 
\verb!VBoxManage -s! for Virtual Box) till the first TCP hit received by the 
test back-end (to make things as smooth as possible, \verb!netcat! was used 
to listen to incoming TCP data).

@@

\paragraph*{Considerations on container start-up in Kubernetes}
Regarding the start-up times in Kubernetes is possible to denote a considerable
difference between the deployment of a SFC with only one element
(\textit{de-facto} only one container) with a single container directly launched
on Docker. The difference, of many seconds, can be easily explained: the
creation of a Docker container, \textit{per se}, is quite fast compared to the
scheduling job the Kubernetes cluster has to do before launching the pod. A
Kubernetes deployment is indeed a rather complex operation than launching a
simple container. When a new deployment is launched on Kubernetes, the operation
initiate with the scheduling of a Pod. A Pod can have several lifecycle
states~\cite{kubePodLifecycle}:
\begin{description}
\item[pending:] The Pod has been accepted by the Kubernetes system, but one or
  more of the Container images has not been created. This includes time before
  being scheduled as well as time spent downloading images over the network,
  which could take a while;
\item[running:] The Pod has been bound to a node, and all of the Containers have
  been created. At least one Container is still running, or is in the process of
  starting or restarting;
\item[succeeded:] All Containers in the Pod have terminated in success, and will
  not be restarted;
\item[failed:] All Containers in the Pod have terminated, and at least one
  Container has terminated in failure. That is, the Container either exited with
  non-zero status or was terminated by the system;
\item[unknown:] For some reason the state of the Pod could not be obtained,
  typically due to an error in communicating with the host of the Pod.
\end{description}

>>>>

Regarding the overall system responsiveness, a metric we considered worth to 
test was the VNF start up time in a docker environment versus one virtualized 
through a common virtual machine system (in this case Virtual Box was chosen). 
To make this simulation as fair as possible, we used the same node (an 
Openstack VM with 32GB of RAM, 8 vCPU and solid state storage) and used the 
same ``boot sequence'' for both the VNFs: first we launched the Astaire 
framework, ensuring its availability to process data and then we notified the 
test machine of the successful boot. The start-up time was measured from the 
beginning of the start-up command (\verb!docker run! for Docker and 
\verb!VBoxManage -s! for Virtual Box) till the first TCP hit received by the 
test back-end (to make things as smooth as possible, \verb!netcat! was used 
to listen to incoming TCP data).

@@

\paragraph*{Considerations on container start-up in Kubernetes}
Regarding the start-up times in Kubernetes is possible to denote a considerable
difference between the deployment of a SFC with only one element
(\textit{de facto} only one container) with a single container directly launched
on Docker. The difference, of many seconds, can be easily explained: the
creation of a Docker container, \textit{per se}, is quite fast compared to the
scheduling job the Kubernetes cluster has to do before launching the pod. A
Kubernetes deployment is indeed a rather complex operation than launching a
simple container. When a new deployment is launched on Kubernetes, the operation
initiate with the scheduling of a Pod. A Pod can have several lifecycle
states~\cite{kubePodLifecycle}:
\begin{description}
\item[pending:] The Pod has been accepted by the Kubernetes system, but one or
  more of the Container images has not been created. This includes time before
  being scheduled as well as time spent downloading images over the network,
  which could take a while;
\item[running:] The Pod has been bound to a node, and all of the Containers have
  been created. At least one Container is still running, or is in the process of
  starting or restarting;
\item[succeeded:] All Containers in the Pod have terminated in success, and will
  not be restarted;
\item[failed:] All Containers in the Pod have terminated, and at least one
  Container has terminated in failure. That is, the Container either exited with
  non-zero status or was terminated by the system;
\item[unknown:] For some reason the state of the Pod could not be obtained,
  typically due to an error in communicating with the host of the Pod.
\end{description}
